Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-12-01 manuscript/bef_stability/appendixB.Rmd
Extract environmental data for fish dynamics

```{r}
sem_variable_table <- tibble(
  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
    ),
  transformation = c(rep("Log base 10", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  interpretation = c("linked to stream size",
    "linked to average temperature",
    "Total species richness over the temporal series",
    "Median of annual link density", "Median of annual average trophic level", "", "",
    "Median of annual total biomass")) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "Variable description and transformation"
  ) %>%
kable_styling(latex_options = c("striped"))
sem_variable_table
```

>>>>

```{r}
sem_variable_table <- tibble(
  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
    ),
  transformation = c(rep("Log base 10", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  interpretation = c("linked to stream size",
    "linked to average temperature",
    "Total species richness over the temporal series",
    "Median of annual link density", "Median of annual average trophic level", "", "",
    "Median of annual total biomass")) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "Variable description and transformation"
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
sem_variable_table
```

### 2020-12-01 manuscript/bef_stability/manuscript.Rmd
Extract environmental data for fish dynamics

```{r}
myload(qt_station, dir = mypath("data"))
matmet_cap <- paste0( 
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
  ", " Inner borders draw the limits of the hydrographic basins. ", "(B) The
  metaweb of the study. Each trophic species (N = 412) is represented by a node
  and each
  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "The species names corresponding to the three digit codes are found in Table
  SXX." ,
  "Yearly temporal series of networks of two stations having respectively a low
  (C) and high (D) temporal stability of biomass. C and D stations have
  respectively biomass stability the closest to the first and third quartile of
  the distribution of the temporal stability of biomass in the dataset,
  respectively ", round(qt_station$bm_std_stab[1],2), " and ",
  round(qt_station$bm_std_stab[2],
    2), ". Point size are proportional to the biomass of the trophic species.")

@@

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. In this case, we
kept only the most frequently used sampling protocol. Then, we selected the
stations that had been sampled ten years or more. There was low heterogeneity of
the sampling month within stations, with the median sampled month being
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to
variability around an equilibrium, which is rarely observed or difficult to
characterize in natural communities, only stations with no temporal trends
in total biomass were selected (detailed in supplementary methods). However, the
results were robust to the relaxation of this hypothesis (Table SXX). These
selection steps resulted in 99 stations distributed over seven hydrographic
basins (Figure \@ref(fig:matmet) A).

@@

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature [REF WILLEM]. Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

The structural equation models were based on Gaussian linear models, all variables
except the connectance and average trophic level
were logged to fulfill model assumptions (see residual plots and data
transformation in supplementary informations, Table SXX). We set the seven
hydrographic basins as a random effect on the intercept of the linear models to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table SXX). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). The paths whose
slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
path values are presented in Table SXX and SXX).

@@

```{r sem-plot, fig.height = 6, fig.cap = sem_caption}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

plot_grid(
  meta_bm_sem_rich, p_bm_sem_rich,
  meta_stab_sem_rich, p_stab_sem_rich,
  labels = LETTERS[1:4], nrow = 2,
  rel_widths = c(1, 1)
)
```

@@

library(kableExtra)
mytable <- kable(full_table,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = caption_sem
  ) %>%
kable_styling(latex_options =c("scale_down")) %>%
add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
column_spec(1:2, width = "3cm") %>%
collapse_rows(columns = 1, valign = "top")
write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
```

>>>>

```{r}
myload(qt_station, dir = mypath("data"))
matmet_cap <- paste0( 
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
  ", " Inner borders draw the limits of the hydrographic basins. ", "(B) The
  metaweb of the study. Each trophic species (N = 412) is represented by a node
  and each
  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "The species names corresponding to the three digit codes are found in Table
  S1." ,
  "Yearly temporal series of networks of two stations having respectively a low
  (C) and high (D) temporal stability of biomass. C and D stations have
  respectively biomass stability the closest to the first and third quartile of
  the distribution of the temporal stability of biomass in the dataset,
  respectively ", round(qt_station$bm_std_stab[1],2), " and ",
  round(qt_station$bm_std_stab[2],
    2), ". Point size are proportional to the biomass of the trophic species.")

@@

The stations where the stream was of intermediate size could be sampled
alternatively with one of the two sampling protocols. In this case, we
kept only the most frequently used sampling protocol. Then, we selected the
stations that had been sampled ten years or more. There was low heterogeneity of
the sampling month within stations, with the median sampled month being
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$. As the concept of community variability referred to
variability around an equilibrium, which is rarely observed or difficult to
characterize in natural communities, only stations with no temporal trends
in total biomass were selected (detailed in supplementary methods). However, the
results were robust to the relaxation of this hypothesis (Figure S7). These
selection steps resulted in 99 stations distributed over seven hydrographic
basins (Figure \@ref(fig:matmet) A).

@@

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (Table S2). Each
fish species had two or three life stages which are delimited by a body size
range (Figure S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Figure S2).

@@

The structural equation models were based on Gaussian linear models, all variables
except the connectance and average trophic level
were logged to fulfill model assumptions (see residual plots and data
transformation in supplementary informations, Figure S5 and S6, Table S5). We set the seven
hydrographic basins as a random effect on the intercept of the linear models to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). The paths whose
slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
path values are presented in Table S7 and S8).

@@

```{r sem-plot, out.width="\\maxwidth", fig.cap = sem_caption, results = "fig.show", cache = FALSE}
#out.height="120%",
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

#plot_grid(
  #meta_bm_sem_rich, p_bm_sem_rich,
  #meta_stab_sem_rich, p_stab_sem_rich,
  #labels = LETTERS[1:4], nrow = 2,
  #rel_widths = c(1, 1)
#)
# Put the panel of Colin
arrow_dir <- mypath("manuscript", "bef_stability","fleches", "figure_sem2")
filename <- list.files(arrow_dir, full.names = TRUE)
mask <- str_match(filename, "\\.svg")[, 1] %>% is.na %>% !.
#filename[mask]
type <- c("bm", "meta_bm", "meta_stab", "stab")
sem_list <- map(filename[mask], function (x) {
  w <- 2400
  img <- magick::image_read_svg(
    path = x, width = w, height=w*1.618)#, density = 600
  p_sem <- cowplot::ggdraw() +
    cowplot::draw_image(img)#, scale = 1.0
  return(p_sem)
})
sem_list %<>% map(., ~.x + theme(plot.margin = unit(x = rep(0, 4), units = "pt")))
names(sem_list) <- type
sem_plot <- plot_grid(
  plotlist = sem_list[c("meta_bm", "bm", "meta_stab", "stab")],
  labels = "AUTO" 
  )
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs",
    "sem_colin.pdf"),
  plot = sem_plot, ncol = 2, nrow = 2,
  base_width = 2.71, base_asp = 1.2 
)
#sem_plot
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "sem_mano.pdf"))
```

@@

library(kableExtra)
mytable <- kable(full_table,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = caption_sem
  ) %>%
kable_styling(latex_options =c("scale_down")) %>%
add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
column_spec(1:2, width = "3cm") %>%
collapse_rows(columns = 1, valign = "top")
#write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
```
